---
title: "Metabolic_Distribution"
author: "Emmi Mueller"
date: "March 8, 2019"
output: pdf_document
---

#Require vegan, fitdistrplus, actuar, and BiocManager with flowFCS
```{r}
rm(list = ls())
getwd()
library('ggpmisc')

package.list <- c('BiocManager', 'vegan', 'fitdistrplus', 'ggplot2', 'car', 'here', 'ggcyto', 'actuar', 'tibble', 'ggpubr', 'scales', 'dplyr', 'ggpmisc') 

for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) { 
    install.packages(package, dependencies = TRUE)
    library(package, character.only=T)
  } }

#BiocManager::valid()
#BiocManager::install("flowCore")
#BiocManager::install("ggcyto")
BiocManager::install()
```

```{r figure_setup}
my.cols <- RColorBrewer::brewer.pal(n = 4, name = "Greys")[3:4]

# Set theme for figures in the paper
theme_set(theme_classic() + 
  theme(axis.title = element_text(size = 16),
        axis.title.x = element_text(margin = margin(t = 15, b = 15)),
        axis.title.y = element_text(margin = margin(l = 15, r = 15)),
        axis.text = element_text(size = 14),
        axis.text.x = element_text(margin = margin(t = 5)),
        axis.text.y = element_text(margin = margin(r = 5)),
        #axis.line.x = element_line(size = 1),
        #axis.line.y = element_line(size = 1),
        axis.line.x = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.x = element_line(size = 1),
        axis.ticks.y = element_line(size = 1),
        axis.ticks.length = unit(.1, "in"),
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        legend.title = element_blank(),
        legend.text = element_text(size = 14),
        strip.text = element_text(size = 14),
        strip.background = element_blank()
        ))
```

#RAC function takes in a list of activity units and returns the list ranked
```{r}
RAC <- function(x = ""){
  x = as.vector(x)
  x.ab = x[x >0]
  rac = x.ab[order(x.ab, decreasing = TRUE)]
  ranks <- as.vector(seq(1,length(rac)))
  rac <- cbind(ranks, rac)
  return(as.data.frame(rac))
}

```
_
```{r}
mempotratio <-function(x = "", green_channel = "", red_channel = ""){
  fcs <- flowCore::read.fcs(file = x)
  flow <- flowCore::exprs(fcs)
  ratio <- as.data.frame(flow[,red_channel] - flow[,green_channel] + (1.5*2330169))
  rac <- RAC(x = ratio)
  ranks <- as.vector(seq(1,length(rac)))
  rac <- cbind(ranks, rac)
  return(rac)
  #scale ranked ratios?
}
```

#process function takes in the name of a fcs file, channel to be saved, and scale and returns a ranked rank activity matrix
```{r}
processmultiple <- function(x = "", channel = "", scale = "", name = "", desc = ""){
  n <- 1
  mynames <- list()
  #make a list with names of cat(name,desc, sep = "_")
  raclist <- list()
  for(file in x){
    mynames <- cbind(mynames, cat(name,desc,sep = "_"))
  }
  for (file in x){
    if(scale == TRUE){
      fcs <- flowCore::read.FCS(file = file, transformation = "scale")
    }
    else{
      fcs <- flowCore::read.FCS(file = file)
    }
    flow <- flowCore::exprs(fcs)
    RSG_H <- as.data.frame(flow[,channel])
    rac <- RAC(x = RSG_H)
    ranks <- as.vector(seq(1,length(rac)))
    rac <- cbind(ranks, rac)
    raclist[[n]] <- as.data.frame(rac)
    n <- n + 1
  }
  names(raclist) <- mynames
  return(raclist)
}
```

```{r}
process <- function(x = "", channel = "", scale = ""){
  if(scale == TRUE){
    fcs <- flowCore::read.FCS(file = x, transformation = "scale", truncate_max_range = FALSE)
  }
  else{
    fcs <- flowCore::read.FCS(file = x, truncate_max_range = FALSE)
  }
  flow <- flowCore::exprs(fcs)
  RSG_H <- as.data.frame(flow[,channel])
  RSG_H <- unlist(RSG_H)
#  rac <- RAC(x = RSG_H)
#  return(rac)
  
  RSG_ab = RSG_H[RSG_H >0]
  return(as.data.frame(RSG_ab))
}
```

#Cdist function takes in a list of activity values and calculates the CDF and returns the CDF and percentage of cells contributing to CDF
```{r}
CDist <- function(x = ""){
  x <- as.vector(x)
  sum <- sum(x)
  rank <- 1
  total <- length(x)
  cdist <- as.vector((x[1]/sum)*100)
  Per <- as.vector((rank/total) * 100)
  for(num in x){
    rank <- rank + 1
    x <- x[-1]
    current <- cdist[length(cdist)] + ((x[1]/sum)*100)
    Per <- c(Per, ((rank/total) *100))
    cdist <- c(cdist, current)
  }
  ranked <- cbind(cdist, Per)
  return(as.data.frame(ranked))

}
```

```{r}
Pareto <- function(x = "", pareto_para = ""){
  head(x)
  pareto <- fitdist(x[ ,2], "pareto", start = list(shape = 0.1, scale = 10))
  pareto_para <- rbind(pareto_para, c(pareto$estimate[1], pareto$estimate[2]))
  return(pareto_para)
}
```


#Titration test for ATP-Red and RSG with Jordan River Samples
```{r}
here()
JR_100 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "A1_JR_100.fcs"))
JR_10 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "B1_JR_10.fcs"))
JR_1 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "C1_JR_1.fcs"))
JR_100_ATP_10 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "A4_JR_100_ATP_10.fcs"))
JR_10_ATP_10 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "B4_JR_10_ATP_10.fcs"))
JR_1_ATP_10 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "C4_JR_1_ATP_10.fcs"))
JR_100_ATP_5 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "D4_JR_100_ATP_5.fcs"))
JR_10_ATP_5 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "A5_JR_10_ATP_5.fcs"))
JR_1_ATP_5 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "B5_JR_1_ATP_5.fcs"))
JR_100_ATP_1 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "C5_JR_100_ATP_1.fcs"))
JR_10_ATP_1 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "D5_JR_10_ATP_1.fcs"))
JR_1_ATP_1 <- flowCore::read.FCS(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "A6_JR_1_ATP_1.fcs"))

JR_100_ATP_Un <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "A1_JR_100.fcs"), "B586-H")
JR_10_ATP_Un <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "B1_JR_10.fcs"), "B586-H")
JR_1_ATP_Un <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "C1_JR_1.fcs"), "B586-H")
JR_100_ATP_10 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "A4_JR_100_ATP_10.fcs"), "B586-H")
JR_10_ATP_10 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "B4_JR_10_ATP_10.fcs"), "B586-H")
JR_1_ATP_10 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "C4_JR_1_ATP_10.fcs"), "B586-H")
JR_100_ATP_5 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "D4_JR_100_ATP_5.fcs"), "B586-H")
JR_10_ATP_5 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "A5_JR_10_ATP_5.fcs"), "B586-H")
JR_1_ATP_5 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "B5_JR_1_ATP_5.fcs"), "B586-H")
JR_100_ATP_1 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "C5_JR_100_ATP_1.fcs"), "B586-H")
JR_10_ATP_1 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "D5_JR_10_ATP_1.fcs"), "B586-H")
JR_1_ATP_1 <- process(here("data","MetDistRA21", "20210713_JR_Titration_RSG_ATP", "A6_JR_1_ATP_1.fcs"), "B586-H")

JR_1_ATP_10_CD <- CDist(JR_1_ATP_10[,1])
JR_1_ATP_5_CD <- CDist(JR_1_ATP_5[,1])
JR_1_ATP_1_CD <- CDist(JR_1_ATP_1[,1])
JR_1_CD <- CDist(JR_1_ATP_Un[,1])
                  

plot(JR_1_CD[,2], JR_1_CD[,1], type = 'p', xlab = "", ylab = "", cex = 0.25, col = "red", yaxt = "n", xaxt = "n")
points(JR_1_ATP_10_CD[,2], JR_1_ATP_10_CD[,1], type = 'p', cex = 0.25)
points(JR_1_ATP_5_CD[,2], JR_1_ATP_5_CD[,1], type = 'p', cex = 0.25)
points(JR_1_ATP_1_CD[,2], JR_1_ATP_1_CD[,1], type = 'p', cex = 0.25, col = "green")
mtext("% of rank-ordered cells \ncontributing to activity", side = 1, line = 2, cex = 0.8)
mtext("Cumulative % \nmembrane potential", side = 2, line = 1.1, cex = 0.8)
axis(2, at = c(0,20,40,60,80,100), labels = c("0","20","40","60","80","100"), cex.axis=0.7, mgp = c(3,0.5,0))
axis(1, cex.axis = 0.7, mgp = c(3,0.5,0), at = c(0,20,40,60,80,100), labels = TRUE)


JR_ATP <- ggplot(JR_100_ATP_Un, aes(x = log(RSG_ab), color = "100", fill = "Unstained"))+
  geom_histogram(binwidth = 0.25)+
  geom_histogram(data = JR_10_ATP_Un, aes(x = log(RSG_ab), color = "10", fill = "Unstained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_1_ATP_Un, aes(x = log(RSG_ab), color = "1", fill = "Unstained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_100_ATP_10, aes(x = log(RSG_ab), color = "100", fill = "Stained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_10_ATP_10, aes(x = log(RSG_ab), color = "10", fill = "Stained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_1_ATP_10, aes(x = log(RSG_ab), color = "1", fill = "Stained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_100_ATP_5, aes(x = log(RSG_ab), color = "100", fill = "Stained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_10_ATP_5, aes(x = log(RSG_ab), color = "10", fill = "Stained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_1_ATP_5, aes(x = log(RSG_ab), color = "1", fill = "Stained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_100_ATP_1, aes(x = log(RSG_ab), color = "100", fill = "Stained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_10_ATP_1, aes(x = log(RSG_ab), color = "10", fill = "Stained"),
                 binwidth = 0.25)+
  geom_histogram(data = JR_1_ATP_1, aes(x = log(RSG_ab), color = "1", fill = "Stained"),
                 binwidth = 0.25)+
  scale_color_manual("Legend Title", limits=c("100", "10", "1"), values = c("black","red", "blue"))+
  scale_fill_manual("Legend Title", limits=c("Unstained", "Stained"),
                     values = c("green", alpha("black", 0.05)))+
  guides(colour = guide_legend(override.aes = list(pch = c(16, 16, 16),
                   fill = c("black", "red", "blue"))))+
  xlab("ATP-H")+
  scale_x_continuous(labels = label_math(expr = 10^.x, format = force))

JR_ATP

ggsave(here("output", "JR_ATP_titration.png"))
ggsave(here("output", "JR_ATP_titration.pdf"))

```
#processing of strains from Jake for QUEEN ratio (V530/B530) and QUEEN ratio plots
```{r}
PBS_04 <- flowCore::read.FCS(here("data", "MetDist_Strains", "20210704_MetDist", "A1_PBS.fcs"))
Ecoli_04 <- flowCore::read.FCS(here("data", "MetDist_Strains", "20210704_MetDist", "B1_Ecoli.fcs"))
QNA_04 <- flowCore::read.FCS(here("data", "MetDist_Strains", "20210704_MetDist", "C1_QNA.fcs"))
QUE7_04 <- flowCore::read.FCS(here("data", "MetDist_Strains", "20210704_MetDist", "D1_QUE7.fcs"))
QUE2_04 <- flowCore::read.FCS(here("data", "MetDist_Strains", "20210704_MetDist", "A2_QUE2.fcs"))
REXYFP_04 <- flowCore::read.FCS(here("data", "MetDist_Strains", "20210704_MetDist", "B2_REXYFP.fcs"))
Peredox_04 <- flowCore::read.FCS(here("data", "MetDist_Strains", "20210704_MetDist", "C2_Peredox.fcs"))
  
QUE2_Ratio <- as.data.frame(flowCore::exprs(QUE2_04)[,c("B530-H", "V530-H")])
QUE2_Ratio$Ratio <- QUE2_Ratio$`V530-H`/QUE2_Ratio$`B530-H`
QUE2_Ratio <- QUE2_Ratio[is.finite(QUE2_Ratio$Ratio) == TRUE,]
QUE7_Ratio <- as.data.frame(flowCore::exprs(QUE7_04)[,c("B530-H", "V530-H")])
QUE7_Ratio$Ratio <- QUE7_Ratio$`V530-H`/QUE7_Ratio$`B530-H`
QUE7_Ratio <- QUE7_Ratio[is.finite(QUE7_Ratio$Ratio) == TRUE,]
QNA_Ratio <- as.data.frame(flowCore::exprs(QNA_04)[,c("B530-H", "V530-H")])
QNA_Ratio$Ratio <- QNA_Ratio$`V530-H`/QNA_Ratio$`B530-H`
QNA_Ratio <- QNA_Ratio[is.finite(QNA_Ratio$Ratio) == TRUE,]
QUE7 <- data.frame(group = "QUE7", value = QUE7_Ratio$Ratio)
QUE2 <- data.frame(group = "QUE2", value = QUE2_Ratio$Ratio)
QNA <- data.frame(group = "QNA", value = QNA_Ratio$Ratio)
ratios <- rbind(QUE7, QUE2, QNA)

QUEEN <- ggplot(data = ratios, aes(x = group, y = value))+
    geom_jitter()+
    ylab("Ratio (405ex/488ex)")+
    xlab("")+
    annotate("text", x = 1, y = 2000, label = mean(QNA_Ratio$Ratio))+
    annotate("text", x = 2, y = 2000, label = mean(QUE2_Ratio$Ratio))+
    annotate("text", x = 3, y = 2000, label = mean(QUE7_Ratio$Ratio))

QUEEN

ggsave(here("output", "QUEEN_ratio.png"))
ggsave(here("output", "QUEEN_ratio.pdf"))

QUEEN_hist <- ggplot(QNA_Ratio, aes(x = Ratio, color = "QNA", fill = "QNA"))+
  geom_histogram(binwidth = 0.25)+
  geom_histogram(data = QUE2_Ratio, aes(x = Ratio, color = "QUE2", fill = "QUE2"),
                 binwidth = 0.25)+
  geom_histogram(data = QUE7_Ratio, aes(x = Ratio, color = "QUE7", fill = "QUE7"),
                 binwidth = 0.25)+
  scale_color_manual("Legend Title", limits=c("QNA", "QUE2", "QUE7"),
                     values = c("black","red", "blue"))+
  scale_fill_manual("Legend Title", limits=c("QNA", "QUE7", "QUE2"),
                    values = alpha(c("black", "red", "blue"), 0.1))+
  guides(colour = guide_legend(override.aes = list(pch = c(16, 16, 16),
                    fill = c("black", "red", "blue"))))+
  xlab("Y615-H")+
  scale_y_log10()

QUEEN_hist

ggsave(here("output", "QUEEN_hist.png"))
ggsave(here("output", "QUEEN_hist.pdf"))
```
#processing of strains from Jake for mCherry and Peredox plots
```{r}
PBS_04_rac_y615 <- process(here("data", "MetDist_Strains", "20210704_MetDist", "A1_PBS.fcs"), "Y615-H")
Ecoli_04_rac_y615 <- process(here("data", "MetDist_Strains", "20210704_MetDist", "B1_Ecoli.fcs"), "Y615-H")
QNA_04_rac_y615 <- process(here("data", "MetDist_Strains", "20210704_MetDist", "C1_QNA.fcs"), "Y615-H")
QUE7_04_rac_y615 <- process(here("data", "MetDist_Strains", "20210704_MetDist", "D1_QUE7.fcs"), "Y615-H")
QUE2_04_rac_y615 <- process(here("data", "MetDist_Strains", "20210704_MetDist", "A2_QUE2.fcs"), "Y615-H")
REXYFP_04_rac_y615 <- process(here("data", "MetDist_Strains", "20210704_MetDist", "B2_REXYFP.fcs"), "Y615-H")
Peredox_04_rac_y615 <- process(here("data", "MetDist_Strains", "20210704_MetDist", "C2_Peredox.fcs"), "Y615-H")



PBS_04_cdist_y615 <- CDist(PBS_04_rac_y615[,2])
Ecoli_04_cdist_y615 <- CDist(Ecoli_04_rac_y615[,2])
QNA_04_cdist_y615 <- CDist(QNA_04_rac_y615[,2])
QUE7_04_cdist_y615 <- CDist(QUE7_04_rac_y615[,2])
QUE2_04_cdist_y615 <- CDist(QUE2_04_rac_y615[,2])
REXYFP_04_cdist_y615 <- CDist(REXYFP_04_rac_y615[,2])
Peredox_04_cdist_y615 <- CDist(Peredox_04_rac_y615[,2])

hist <- hist(QNA_04_rac_y615[,2], breaks = 1000)
hist.dat <- data.frame(hist$mids,hist$counts,hist$density)
colnames(hist.dat)<- c("mids", "counts", "density")
plot(log10(hist.dat$mids), log10(hist.dat$density))


mCherry <- ggplot(PBS_04_rac_y615, aes(x = log(rac), color = "PBS", fill = "PBS"))+
  geom_histogram(binwidth = 0.25)+
  geom_histogram(data = Ecoli_04_rac_y615, aes(x = log(rac), color = "Ecoli", fill = "Ecoli"),
                 binwidth = 0.25)+
  geom_histogram(data = Peredox_04_rac_y615, aes(x = log(rac), color = "Peredox", fill = "Peredox"),
                 binwidth = 0.25)+
  geom_histogram(data =   QNA_04_rac_y615, aes(x = log(rac), color = "QNA", fill = "QNA"),
                 binwidth = 0.25)+
  geom_histogram(data =   QUE7_04_rac_y615, aes(x = log(rac), color = "QUE7", fill = "QUE7"),
                 binwidth = 0.25)+
  geom_histogram(data =   QUE2_04_rac_y615, aes(x = log(rac), color = "QUE2", fill = "QUE2"),
                 binwidth = 0.25)+
  geom_histogram(data =   REXYFP_04_rac_y615, aes(x = log(rac), color = "REXYFP", fill = "REXYFP"),
                 binwidth = 0.25)+
  scale_color_manual("Legend Title", limits=c("PBS", "Ecoli", "Peredox", "QNA", "QUE7", "QUE2", "REXYFP"),
                     values = c("black","red", "blue", "green", "orange", "yellow", "purple"))+
  scale_fill_manual("Legend Title", limits=c("PBS", "Ecoli", "Peredox", "QNA", "QUE7", "QUE2", "REXYFP"),
                    values = alpha(c("black", "red", "blue", "green", "orange", "yellow", "purple"), 0.1))+
  guides(colour = guide_legend(override.aes = list(pch = c(16, 16, 16, 16, 16, 16, 16),
                    fill = c("black", "red", "blue", "green", "orange", "yellow", "purple"))))+
  xlab("Y615-H")+
  scale_x_continuous(labels = label_math(expr = 10^.x, format = force))

mCherry

ggsave(here("output", "mCherry_counts.png"))
ggsave(here("output", "mCherry_counts.pdf"))
```


#GROWTH CURVE ANALYSIS

##Process growth rate fcs files
```{r}
aa_rac_Ecoli_GC_1 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T1_S.fcs"), "BL1-H")
aa_rac_Ecoli_GC_2 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T2_S.fcs"), "BL1-H")
aa_rac_Ecoli_GC_3 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T3_S.fcs"), "BL1-H")
aa_rac_Ecoli_GC_4 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T4_S.fcs"), "BL1-H")
aa_rac_Ecoli_GC_5 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T5_S.fcs"), "BL1-H")
aa_rac_Ecoli_GC_6 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T6_S.fcs"), "BL1-H")
aa_rac_Ecoli_GC_7 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T7_S.fcs"), "BL1-H")

aa_Cdist_Ecoli_GC_1 <- CDist(RAC(x = unlist(aa_rac_Ecoli_GC_1$RSG_ab))[,2])
aa_Cdist_Ecoli_GC_2 <- CDist(RAC(x = unlist(aa_rac_Ecoli_GC_2$RSG_ab))[,2])
aa_Cdist_Ecoli_GC_3 <- CDist(RAC(x = unlist(aa_rac_Ecoli_GC_3$RSG_ab))[,2])
aa_Cdist_Ecoli_GC_4 <- CDist(RAC(x = unlist(aa_rac_Ecoli_GC_4$RSG_ab))[,2])
aa_Cdist_Ecoli_GC_5 <- CDist(RAC(x = unlist(aa_rac_Ecoli_GC_5$RSG_ab))[,2])
aa_Cdist_Ecoli_GC_6 <- CDist(RAC(x = unlist(aa_rac_Ecoli_GC_6$RSG_ab))[,2])
aa_Cdist_Ecoli_GC_7 <- CDist(RAC(x = unlist(aa_rac_Ecoli_GC_7$RSG_ab))[,2])

ra_rac_Ecoli_GC_1 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T1_S.fcs"), "BL1-H", TRUE)
ra_rac_Ecoli_GC_2 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T2_S.fcs"), "BL1-H", TRUE)
ra_rac_Ecoli_GC_3 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T3_S.fcs"), "BL1-H", TRUE)
ra_rac_Ecoli_GC_4 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T4_S.fcs"), "BL1-H", TRUE)
ra_rac_Ecoli_GC_5 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T5_S.fcs"), "BL1-H", TRUE)
ra_rac_Ecoli_GC_6 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T6_S.fcs"), "BL1-H", TRUE)
ra_rac_Ecoli_GC_7 <- process(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "Specimen1_T7_S.fcs"), "BL1-H", TRUE)
ra_Cdist_Ecoli_GC_1 <- CDist(RAC(x = unlist(ra_rac_Ecoli_GC_1$RSG_ab))[,2])
ra_Cdist_Ecoli_GC_2 <- CDist(RAC(x = unlist(ra_rac_Ecoli_GC_2$RSG_ab))[,2])
ra_Cdist_Ecoli_GC_3 <- CDist(RAC(x = unlist(ra_rac_Ecoli_GC_3$RSG_ab))[,2])
ra_Cdist_Ecoli_GC_4 <- CDist(RAC(x = unlist(ra_rac_Ecoli_GC_4$RSG_ab))[,2])
ra_Cdist_Ecoli_GC_5 <- CDist(RAC(x = unlist(ra_rac_Ecoli_GC_5$RSG_ab))[,2])
ra_Cdist_Ecoli_GC_6 <- CDist(RAC(x = unlist(ra_rac_Ecoli_GC_6$RSG_ab))[,2])
ra_Cdist_Ecoli_GC_7 <- CDist(RAC(x = unlist(ra_rac_Ecoli_GC_7$RSG_ab))[,2])

OD600_Ecoli_GC <- read.table(here("data", "GrowthCurve", "EAM_20190531_GrowthCurve", "20190531_EAM_GrowthCurve.txt"), header = TRUE, sep = "\t")

```

#OD600 vs. Abundance curves and fits
```{r}
#fit logistic growth model to growth curve for OD600
coef(lm(logit(OD600_Ecoli_GC$OD600/0.9)~OD600_Ecoli_GC$minutes))
growthcurve_OD<-nls(OD600_Ecoli_GC$OD600~phi1/(1+exp(-(phi2+phi3*OD600_Ecoli_GC$minutes))),
 start=list(phi1=0.9,phi2=-2.805,phi3=0.031), data = OD600_Ecoli_GC, trace=TRUE)
phi1_OD<-coef(growthcurve_OD)[1]
phi2_OD<-coef(growthcurve_OD)[2]
phi3_OD<-coef(growthcurve_OD)[3]
x<-c(min(OD600_Ecoli_GC$minutes):max(OD600_Ecoli_GC$minutes))
y<-phi1_OD/(1+exp(-(phi2_OD+phi3_OD*x)))
predict_OD600<-data.frame(x,y)

#fit logistic growth model to growth curve for abs_count
coef(lm(logit(OD600_Ecoli_GC$abs_count/490000000)~OD600_Ecoli_GC$minutes))
growthcurve_ac<-nls(OD600_Ecoli_GC$abs_count~phi1/(1+exp(-(phi2+phi3*OD600_Ecoli_GC$minutes))),
 start=list(phi1=490000000,phi2=-3.162,phi3=0.031), data = OD600_Ecoli_GC, trace=TRUE)
phi1_ac<-coef(growthcurve_ac)[1]
phi2_ac<-coef(growthcurve_ac)[2]
phi3_ac<-coef(growthcurve_ac)[3]
y<-phi1_ac/(1+exp(-(phi2_ac+phi3_ac*x)))
predict_abscount<-data.frame(x,y)
```

#Growth Curve OD600 vs. Abs count fits
```{r}
#generate png file
png(here("output", "GrowthCurve.OD600_abscount_fits.png"),
     width = 900, height = 900, res = 96*2)

par(fig=c(0,1,0.35,1))
color <- c("red", "orange", "yellow", "green", "cyan", "blue", "purple")
plot(OD600_Ecoli_GC$minutes, OD600_Ecoli_GC$OD600, col = color, pch = 19, cex = 1, ylab = "", xlab= "", yaxt = "n", xaxt = "n")
mtext("Time(mins)", side = 1, line = 1.1, cex = 0.8)
mtext("OD600", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))
lines(predict_OD600)

par(fig=c(0,1,0,0.65), new = TRUE)
color <- c("red", "orange", "yellow", "green", "cyan", "blue", "purple")
plot(OD600_Ecoli_GC$minutes, OD600_Ecoli_GC$abs_count, col = color, pch = 19, cex = 1, ylab = "", xlab= "", yaxt = "n", xaxt = "n")
mtext("Time(mins)", side = 1, line = 1.1, cex = 0.8)
mtext("abs. count", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))
lines(predict_abscount)

dev.off()
```

#GC lines relative abundance CDF and RAC using OD600
```{r}
#generate png file
png(here("output", "GrowthCurve.RSGdistribution.png"),
     width = 900, height = 900, res = 96*2)

par(fig=c(0,1,0.4,1))
color <- c("red", "orange", "yellow", "green", "cyan", "blue", "purple")
plot(OD600_Ecoli_GC$minutes, OD600_Ecoli_GC$OD600, col = color, pch = 19, cex = 1, ylab = "", xlab= "", yaxt = "n", xaxt = "n")
mtext("Time(mins)", side = 1, line = 1.1, cex = 0.8)
mtext("OD600", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))
lines(predict_OD600)

par(fig=c(0,0.55,0,0.65), new=TRUE)
plot(ra_rac_Ecoli_GC_7[,1], log(ra_rac_Ecoli_GC_7[,2]), type = 'p', xlab = "", ylab = "", cex = 0.25, col = "red", yaxt = "n", xaxt = "n")
mtext("Rank in activity", side = 1, line = 1.1, cex = 0.8)
mtext("log(RSG-H value)", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7, mgp = c(3, 0.5, 0))
points(ra_rac_Ecoli_GC_2[,1], log(ra_rac_Ecoli_GC_2[,2]), type = 'p', cex = 0.25, col = "orange")
points(ra_rac_Ecoli_GC_3[,1], log(ra_rac_Ecoli_GC_3[,2]), type = 'p', cex = 0.25, col = "yellow")
points(ra_rac_Ecoli_GC_4[,1], log(ra_rac_Ecoli_GC_4[,2]), type = 'p', cex = 0.25, col = "green")
points(ra_rac_Ecoli_GC_5[,1], log(ra_rac_Ecoli_GC_5[,2]), type = 'p', cex = 0.25, col = "cyan")
points(ra_rac_Ecoli_GC_6[,1], log(ra_rac_Ecoli_GC_6[,2]), type = 'p', cex = 0.25, col = "blue")
points(ra_rac_Ecoli_GC_1[,1], log(ra_rac_Ecoli_GC_1[,2]), type = 'p', cex = 0.25, col = "purple")
box()

par(fig=c(0.45,1,0,0.65), new=TRUE)
plot(ra_Cdist_Ecoli_GC_1[,2], ra_Cdist_Ecoli_GC_1[,1], type = 'p', xlab = "", ylab = "", cex = 0.25, col = "red", yaxt = "n", xaxt = "n")
mtext("% of rank-ordered cells \ncontributing to activity", side = 1, line = 2, cex = 0.8)
mtext("Cumulative % \nRSG activity", side = 2, line = 1.1, cex = 0.8)
axis(2, at = c(0,20,40,60,80,100), labels = c("0","20","40","60","80","100"), cex.axis=0.7, mgp = c(3,0.5,0))
axis(1, cex.axis = 0.7, mgp = c(3,0.5,0), at = c(0,20,40,60,80,100), labels = TRUE)
points(ra_Cdist_Ecoli_GC_2[,2], ra_Cdist_Ecoli_GC_2[,1], type = 'p', cex = 0.25, col = "orange")
points(ra_Cdist_Ecoli_GC_3[,2], ra_Cdist_Ecoli_GC_3[,1], type = 'p', cex = 0.25, col = "yellow")
points(ra_Cdist_Ecoli_GC_4[,2], ra_Cdist_Ecoli_GC_4[,1], type = 'p', cex = 0.25, col = "green")
points(ra_Cdist_Ecoli_GC_5[,2], ra_Cdist_Ecoli_GC_5[,1], type = 'p', cex = 0.25, col = "cyan")
points(ra_Cdist_Ecoli_GC_6[,2], ra_Cdist_Ecoli_GC_6[,1], type = 'p', cex = 0.25, col = "blue")
points(ra_Cdist_Ecoli_GC_7[,2], ra_Cdist_Ecoli_GC_7[,1], type = 'p', cex = 0.25, col = "purple")
box()

dev.off()

```



#Growth curve pareto distribution fits against OD
```{r}
OD600 <- function(x) (phi1_OD/(1+exp(-(phi2_OD+phi3_OD*x))))
curve(OD600, 0, 250, ylab = "OD600=f(minutes)")
deriv_OD600 <- function(x) {}
body(deriv_OD600) <- D(body(OD600), 'x')
curve(deriv_OD600, 0, 250, ylab = "f'(minutes)")
deriv <- deriv_OD600(OD600_Ecoli_GC$minutes)

abs_count <- function(x) (phi1_ac/(1+exp(-(phi2_ac+phi3_ac*x))))
curve(abs_count, 0, 250, ylab = "abs_count=f(minutes)")
deriv_abs_Count <- function(x){}
body(deriv_abs_Count) <- D(body(abs_count), 'x')
curve(deriv_abs_Count, 0, 250, ylab = "f'(minutes)")
der_abs_count <- deriv_abs_Count(OD600_Ecoli_GC$minutes)

CG <- list(ra_rac_Ecoli_GC_1, ra_rac_Ecoli_GC_2, ra_rac_Ecoli_GC_3, ra_rac_Ecoli_GC_4, ra_rac_Ecoli_GC_5, ra_rac_Ecoli_GC_6, ra_rac_Ecoli_GC_7)
pareto_para <- data.frame()
for(x in CG){
  pareto_para <- Pareto(x, pareto_para)
}

GC <- data.frame(deriv, OD600_Ecoli_GC$OD600, OD600_Ecoli_GC$abs_count, pareto_para)
names(GC) <- c("SGR", "OD600", "abs_count", "shape", "scale")
plot(GC$abs_count, GC$scale)

png(here("output", "GrowthCurve.Pareto_parameters.png"),
     width = 900, height = 900, res = 96*2)

par(fig=c(0,0.5,0.5,1))
plot(GC$OD600, log(GC$shape), type = 'p', pch = 19, ylab = "", xlab = "", yaxt = "n", xaxt = "n", col = "red")
mtext("OD600", side = 1, line = 1.2, cex = 0.8)
mtext("log(shape)", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))
par(fig=c(0.5,1,0.5,1), new = TRUE)
plot(GC$OD600, log(GC$scale), type = 'p', pch = 19, ylab = "", xlab = "", yaxt = "n", xaxt = "n", col = "red")
mtext("OD600", side = 1, line = 1.2, cex = 0.8)
mtext("log(scale)", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))

par(fig=c(0,0.5,0.25,0.75), new = TRUE)
plot(GC$SGR, log(GC$shape), type = 'p', pch = 19, ylab = "", xlab = "", yaxt = "n", xaxt = "n", col = "blue")
mtext("?", side = 1, line = 1.2, cex = 0.8)
mtext("log(shape)", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))
par(fig=c(0.5,1,0.25,0.75), new = TRUE)
plot(GC$SGR, log(GC$scale), type = 'p', pch = 19, ylab = "", xlab = "", yaxt = "n", xaxt = "n", col = "blue")
mtext("?", side = 1, line = 1.2, cex = 0.8)
mtext("log(scale)", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))

par(fig=c(0,0.5,0,0.5), new = TRUE)
plot(GC$abs_count, log(GC$shape), type = 'p', pch = 19, ylab = "", xlab = "", yaxt = "n", xaxt = "n")
mtext("abs. count", side = 1, line = 1.2, cex = 0.8)
mtext("log(shape)", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))
par(fig=c(0.5,1,0,0.5), new = TRUE)
plot(GC$abs_count, log(GC$scale), type = 'p', pch = 19, ylab = "", xlab = "", yaxt = "n", xaxt = "n")
mtext("abs.count", side = 1, line = 1.2, cex = 0.8)
mtext("log(scale)", side = 2, line = 1.1, cex = 0.8)
axis(2,cex.axis=0.7,  mgp = c(3, 0.5, 0))
axis(1, cex.axis = 0.7,  mgp = c(3, 0.5, 0))

dev.off()

```


#fcs LINES

#Process fcs lines for and return ranked lists
```{r}
#relative abundance
ra_rac_Spo0A_1day_S1 <- process(here("data", "MURI", "EAM_20190403_MURI_1day", "Stained_0S1.fcs"), "BL1-H", TRUE)
ra_rac_Spo0A_10day_S1 <- process(here("data", "MURI", "EAM_20190403_MURI_10day", "Specimen1_1S2.fcs"), "BL1-H", TRUE)
ra_rac_Spo0A_100day_S1 <- process(here("data", "MURI", "EAM_20190403_MURI_100day", "Stained_2S1-1.fcs"), "BL1-H", TRUE)
ra_Cdist_Spo0A_1day_S1 <- CDist(ra_rac_Spo0A_1day_S1[,2])
ra_Cdist_Spo0A_10day_S1 <- CDist(ra_rac_Spo0A_10day_S1[,2])
ra_Cdist_Spo0A_100day_S1 <- CDist(ra_rac_Spo0A_100day_S1[,2])

#absolute abundance
aa_rac_Spo0A_1day_S1 <- process(here("data", "MURI", "EAM_20190403_MURI_1day", "Stained_0S1.fcs"), "BL1-H")
aa_rac_Spo0A_10day_S1 <- process(here("data", "MURI", "EAM_20190403_MURI_10day", "Specimen1_1S2.fcs"), "BL1-H")
aa_rac_Spo0A_100day_S1 <- process(here("data", "MURI", "EAM_20190403_MURI_100day", "Stained_2S1-1.fcs"), "BL1-H")
aa_Cdist_Spo0A_1day_S1 <- CDist(aa_rac_Spo0A_1day_S1[,2])
aa_Cdist_Spo0A_10day_S1 <- CDist(aa_rac_Spo0A_10day_S1[,2])
aa_Cdist_Spo0A_100day_S1 <- CDist(aa_rac_Spo0A_100day_S1[,2])

```
#fit lognormal and poisson distributions for muri data
```{r}
aa_1day_rare <- sample_n(aa_rac_Spo0A_1day_S1, length(aa_rac_Spo0A_100day_S1[,2]))
aa_10day_rare <- sample_n(aa_rac_Spo0A_10day_S1,length(aa_rac_Spo0A_100day_S1[,2]))
aa_1day_rare <- RAC(aa_1day_rare[,2])
aa_10day_rare <- RAC(aa_10day_rare[,2])
aa_Cdist_1day_rare <- CDist(aa_1day_rare[,2])
aa_Cdist_10day_rare <- CDist(aa_10day_rare[,2])

# create a vector of histogram breaks
x_1 <- as.integer(seq(0,max(aa_1day_rare[,2]),length=100))
x_10 <- as.integer(seq(0, max(aa_10day_rare[,2]), length=100))
x_100 <- as.integer(seq(0, max(aa_rac_Spo0A_100day_S1[,2]), length = 100))

# histogram the data
hst_1 <- hist(aa_1day_rare[,2], breaks=x_1)
hst_10 <- hist(aa_10day_rare[,2], breaks = x_10)
hst_100 <- hist(aa_rac_Spo0A_100day_S1[,2], breaks = x_100)

# # fit a lognormal distribution
# fit_lognormal_100 <- fitdistr(as.integer(hst_100$counts),"lognormal")
# fit_lognormal_10 <- fitdistr(as.integer(hst_10$mids), "lognormal")
# fit_lognormal_1 <- fitdistr(as.integer(hst_1$mids), "lognormal")
# fit_poisson_1 <- fitdistr(as.integer(hst_1$counts), "poisson")
# fit_poisson_10 <- fitdistr(as.integer(hst_10$counts), "poisson")
# fit_poisson_100 <- fitdistr(as.integer(hst_100$counts), "poisson")
# 
# AIC(fit_lognormal_100, fit_poisson_100)
# AIC(fit_lognormal_10, fit_poisson_10)
# AIC(fit_lognormal_1, fit_poisson_1)
# 
# # generate values given our fit parameters
# fit_1 <- dlnorm(x_1, fit_lognormal_1$estimate['meanlog'], fit_lognormal_1$estimate['sdlog'])
# fit_10 <- dlnorm(x_10, fit_lognormal_10$estimate['meanlog'], fit_lognormal_10$estimate['sdlog'])
# fit_100 <- dlnorm(x_100, fit_lognormal_100$estimate['meanlog'], fit_lognormal_100$estimate['sdlog'])
# fit_1 <- dpois(x_1, fit_poisson_1$estimate['lambda'])
# fit_10 <- dpois(x_10, fit_poisson_10$estimate['lambda'])
# fit_100 <- dpois(x_100, fit_poisson_100$estimate['lambda'])
# 
# # plot the fit and original distributions
# 
# plot(x_1, fit_1, type="l", ylab="Density",xlab="X")
# title(main = "Density histogram with lognormal fit")
# lines(hst_1$mid, hst_1$density, type="l", col="red")
# legend(8,0.15,legend=c("Fit","Data"),lty=c(1,1),col=c("black","red"))
# 
# plot(x_10, fit_10, type="l", ylab="Density", xlab="X", xlim = c(0, max(hst_10$mids)), ylim = c(0, max(hst_10$density)))
# title(main = "Density histogram with lognormal fit")
# lines(hst_10$mid, hst_10$density, type="l", col="red")
# legend(8,0.15,legend=c("Fit","Data"),lty=c(1,1),col=c("black","red"))
# 
# plot(x_100, fit_100, type="l", ylab="Density",
#      xlab="X", ylim=c(0,max(hst_100$density)), xlim=c(0,max(hst_100$mid)))
# title(main = "Density histogram with lognormal fit")
# lines(hst_100$mid, hst_100$density, type="l", col="red")
# legend(8,0.15,legend=c("Fit","Data"),lty=c(1,1),col=c("black","red"))

```

#CDF of subsampled muri data
```{r}

png(here("output", "MURI.Spo0A_RSG_aaCDF_rare.png"),
     width = 1800, height = 900, res = 96*2)

par(fig=c(0,0.5,0,1))

plot(aa_rac_Spo0A_100day_S1[,1], log(aa_rac_Spo0A_100day_S1[,2]), type = 'p', axes = F, xlab = "Rank in activity", ylab = "", las = 1, cex.lab = 1.4, cex.axis = 1.25, col = "blue")
mtext("log(RSG-H value)", side = 2, line = 3, cex = 1.4)
points(aa_10day_rare[,1], log(aa_10day_rare[,2]), type = 'p', col = "red")
points(aa_1day_rare[,1], log(aa_1day_rare[,2]), type = 'p', col = "black")
legend(10000,4.5, c("1 day", "10 day", "100 day"), c("black", "red", "blue"), cex = 1)
box()
axis(side = 1, labels = T, cex.axis = 1.25)
axis(side = 2, las = 1, cex.axis = 1.25)

par(fig=c(0.5,1,0,1), new = TRUE)

plot(aa_Cdist_Spo0A_100day_S1[,2], aa_Cdist_Spo0A_100day_S1[,1], type = 'p', axes = F, xlab = "", ylab = "", las = 1, col = "blue")
mtext("% of rank-ordered cells \n contributing to activity", side = 1, line = 3.5)
mtext("Cumulative % \n RedoxSensor Green activity", side = 2, line = 2.5)
points(aa_Cdist_10day_rare[,2], aa_Cdist_10day_rare[,1], type = 'p', col = "red", cex = 0.75)
points(aa_Cdist_1day_rare[,2], aa_Cdist_1day_rare[,1], type = 'p', col = "black", cex = 0.75)
abline(1,1)
box()
axis(side = 1, labels = T)
axis(side = 2, las = 1)
legend(65,30, c("1 day", "10 day", "100 day"), c("black", "red", "blue"))
text(90,80, "1:1")

mtext("Absolute abundance", outer = TRUE, cex = 2, line =-2.5)

dev.off()

hist <- hist(aa_rac_Spo0A_100day_S1[,2], breaks = 100)
hist.dat <- data.frame(log10(hist$mids),log10(hist$counts),log10(hist$density))
colnames(hist.dat)<- c("mids", "counts", "density")
hist.dat <- hist.dat[is.finite(hist.dat$density),]
lm <- lm(hist.dat$density~hist.dat$mids)
summary(lm)
plot(hist.dat$density ~ hist.dat$mids)
abline(lm)

# fit_1_hist <- ggplot(aa_rac_Spo0A_100day_S1, aes(aa_rac_Spo0A_100day_S1[,2]))+
#   geom_histogram(binwidth = 10)+
#   xlab("Tau")+
#   ylab("Biomass Production (uM C/hr)")+
#   geom_smooth(method = "lm", formula = y~x)+
#   stat_poly_eq(aes(label =  paste(stat(rr.label), "*\" and \"*", stat(p.value.label), sep = "")),
#                formula = y~x, parse = TRUE, size = 4)+
#   scale_x_continuous(labels = label_math(expr = 10^.x, format = force))
# 
# fit_1_hist
```

# Relative and Absolute Abundance fcs lines
```{r}
png(here("output", "MURI.Spo0A_RSG_ra_aa.png"),
     width = 1800, height = 900, res = 96*2)

par(fig=c(0,0.5,0,1))

plot(ra_rac_Spo0A_1day_S1[,1], log(ra_rac_Spo0A_1day_S1[,2]), type = 'p', axes = F, xlab = "Rank in activity", ylab = "", las = 1, cex.lab = 1.4, cex.axis = 1.25)
mtext("log(RSG-H value)", side = 2, line = 3, cex = 1.4)
mtext("Relative abundance", side = 3, line = 1, cex = 2)
points(ra_rac_Spo0A_10day_S1[,1], log(ra_rac_Spo0A_10day_S1[,2]), type = 'p', col = "red")
points(ra_rac_Spo0A_100day_S1[,1], log(ra_rac_Spo0A_100day_S1[,2]), type = 'p', col = "blue")
box()
axis(side = 1, labels = T, cex.axis = 1.25)
axis(side = 2, las = 1, cex.axis = 1.25)

par(fig=c(0.5,1,0,1), new = TRUE)

plot(aa_rac_Spo0A_1day_S1[,1], log(aa_rac_Spo0A_1day_S1[,2]), type = 'p', axes = F, xlab = "Rank in activity", ylab = "", las = 1, cex.lab = 1.4, cex.axis = 1.25)
mtext("log(RSG-H value)", side = 2, line = 3, cex = 1.4)
mtext("Absolute abundance", side = 3, line = 1, cex = 2)
points(aa_rac_Spo0A_10day_S1[,1], log(aa_rac_Spo0A_10day_S1[,2]), type = 'p', col = "red")
points(aa_rac_Spo0A_100day_S1[,1], log(aa_rac_Spo0A_100day_S1[,2]), type = 'p', col = "blue")
legend(10000,4.5, c("1 day", "10 day", "100 day"), c("black", "red", "blue"), cex = 1)
box()
axis(side = 1, labels = T, cex.axis = 1.25)
axis(side = 2, las = 1, cex.axis = 1.25)

dev.off()
```


```{r}
#MURI lines absolute abundance CDF and RAC
png(here("output", "MURI.Spo0A_RSG_aaCDF.png"),
     width = 1800, height = 900, res = 96*2)

par(fig=c(0,0.5,0,1))

plot(aa_rac_Spo0A_1day_S1[,1], log(aa_rac_Spo0A_1day_S1[,2]), type = 'p', axes = F, xlab = "", ylab = "", las = 1, ylim = c(0,15))
mtext("Rank in activity", side = 1, line = 2.75, cex = 1)
mtext("log(RedoxSensor Green activity)", side = 2, line = 2.75, cex = 1)
points(aa_rac_Spo0A_10day_S1[,1], log(aa_rac_Spo0A_10day_S1[,2]), type = 'p', col = "red", cex = 0.75)
points(aa_rac_Spo0A_100day_S1[,1], log(aa_rac_Spo0A_100day_S1[,2]), type = 'p', col = "blue", cex = 0.75)
box()
axis(side = 1, labels = T)
axis(side = 2, las = 1)

par(fig=c(0.5,1,0,1), new = TRUE)


plot(aa_Cdist_Spo0A_1day_S1[,2], aa_Cdist_Spo0A_1day_S1[,1], type = 'p', axes = F, xlab = "", ylab = "", las = 1)
mtext("% of rank-ordered cells \n contributing to activity", side = 1, line = 3.5)
mtext("Cumulative % \n RedoxSensor Green activity", side = 2, line = 2.5)
points(aa_Cdist_Spo0A_10day_S1[,2], aa_Cdist_Spo0A_10day_S1[,1], type = 'p', col = "red", cex = 0.75)
points(aa_Cdist_Spo0A_100day_S1[,2], aa_Cdist_Spo0A_100day_S1[,1], type = 'p', col = "blue", cex = 0.75)
abline(1,1)
box()
axis(side = 1, labels = T)
axis(side = 2, las = 1)
legend(65,30, c("1 day", "10 day", "100 day"), c("black", "red", "blue"))
text(90,80, "1:1")

mtext("Absolute abundance", outer = TRUE, cex = 2, line =-2.5)

dev.off()
```

##Figure for MURI Equipment Grant Report (relative abundance activity)
```{r}
#MURI lines relative abundance CDF and RAC
png(here("output", "MURI.Spo0A_RSG_raCDF.png"),
     width = 1800, height = 900, res = 96*2)

par(fig=c(0,0.5,0,1))

plot(ra_rac_Spo0A_1day_S1[,1], log(ra_rac_Spo0A_1day_S1[,2]), type = 'p', axes = F, xlab = "", ylab = "", las = 1, ylim = c(-15,0))
mtext("Rank in activity", side = 1, line = 2.75, cex = 1)
mtext("log(RedoxSensor Green activity)", side = 2, line = 2.75, cex = 1)
points(ra_rac_Spo0A_10day_S1[,1], log(ra_rac_Spo0A_10day_S1[,2]), type = 'p', col = "red", cex = 0.75)
points(ra_rac_Spo0A_100day_S1[,1], log(ra_rac_Spo0A_100day_S1[,2]), type = 'p', col = "blue", cex = 0.75)
box()
axis(side = 1, labels = T)
axis(side = 2, las = 1)

par(fig=c(0.5,1,0,1), new = TRUE)

plot(ra_Cdist_Spo0A_1day_S1[,2], ra_Cdist_Spo0A_1day_S1[,1], type = 'p', axes = F, xlab = "", ylab = "", las = 1)
mtext("% of rank-ordered cells \n contributing to activity", side = 1, line = 3.5)
mtext("Cumulative % \n RedoxSensor Green activity", side = 2, line = 2.5)
points(ra_Cdist_Spo0A_10day_S1[,2], ra_Cdist_Spo0A_10day_S1[,1], type = 'p', col = "red", cex = 0.75)
points(ra_Cdist_Spo0A_100day_S1[,2], ra_Cdist_Spo0A_100day_S1[,1], type = 'p', col = "blue", cex = 0.75)
legend(65,30, c("1 day", "10 day", "100 day"), c("black", "red", "blue"))
abline(1,1)
text(90,80, "1:1")
box()
axis(side = 1, labels = T)
axis(side = 2, las = 1)
mtext("Relative abundance", outer = TRUE, cex = 2, line =-2.5)
dev.off()
```



