---
title: "Metabolic_Distribution"
author: "Emmi Mueller"
date: "March 8, 2019"
output: pdf_document
---

#Require vegan, fitdistrplus, actuar, and BiocManager with flowFCS
```{r}
rm(list = ls())
getwd()
library("BiocManager")
BiocManager::valid()
BiocManager::install()
library("vegan")
library("fitdistrplus")
library("actuar")

```

#RAC function takes in a list of activity units and returns the list ranked
```{r}
RAC <- function(x = ""){
  x = as.vector(x)
  x.ab = x[x >0]
  x.ab.ranked = x.ab[order(x.ab, decreasing = TRUE)]
  return(x.ab.ranked)
}


```

#process function takes in the name of a fcs file, channel to be saved, and scale and returns a ranked rank activity matrix
```{r}
process <- function(x = "", channel = "", scale = ""){
  if(scale == TRUE){
    fcs <- flowCore::read.FCS(file = x, transformation = "scale")
  }
  else{
    fcs <- flowCore::read.FCS(file = x)
  }
  flow <- flowCore::exprs(fcs)
  RSG_H <- as.data.frame(flow[,channel])
  rac <- RAC(x = RSG_H)
  ranks <- as.vector(seq(1,length(rac)))
  rac <- cbind(ranks, rac)
  return(rac)
}
```

#Cdist function takes in a list of activity values and calculates the CDF and returns the CDF and percentage of cells contributing to CDF
```{r}
CDist <- function(x = ""){
  x <- as.vector(x)
  sum <- sum(x)
  rank <- 1
  total <- length(x)
  cdist <- as.vector((x[1]/sum)*100)
  Per <- as.vector((rank/total) * 100)
  print(length(x))
  print(length(cdist))
  for(num in x){
    rank <- rank + 1
    x <- x[-1]
    current <- cdist[length(cdist)] + ((x[1]/sum)*100)
    Per <- c(Per, ((rank/total) *100))
    cdist <- c(cdist, current)
  }
  ranked <- cbind(cdist, Per)
  return(ranked)

}
```


# Relative and Absolute Abundance MURI lines
```{r}
plot.new()
par(mar = c(5,5,4,1)+0.1, mfrow = c(1,2))

rac_0S1 <- process("../data/FCS/EAM_20190403_MURI_1day/Stained_0S1.fcs", "BL1-H", TRUE)
rac_1S1 <- process("../data/FCS/EAM_20190403_MURI_10day/Specimen1_1S2.fcs", "BL1-H", TRUE)
rac_2S1 <- process("../data/FCS/EAM_20190403_MURI_100day/Stained_2S1-1.fcs", "BL1-H", TRUE)
opar <- par(no.readonly = TRUE)
par(mar = c(5,6,4,2)+0.1)
plot(rac_0S1[,1], log(rac_0S1[,2]), type = 'p', axes = F, xlab = "Rank in activity", ylab = "", main = "Relative", las = 1, cex.lab = 1.4, cex.axis = 1.25)
mtext("log(RSG-H value)", side = 2, line = 3, cex.lab = 1.4)
points(rac_1S1[,1], log(rac_1S1[,2]), type = 'p', col = "red")
points(rac_2S1[,1], log(rac_2S1[,2]), type = 'p', col = "blue")

box()
axis(side = 1, labels = T, cex.axis = 1.25)
axis(side = 2, las = 1, cex.axis = 1.25)

par <- opar

rac_0S1 <- process("../data/FCS/EAM_20190403_MURI_1day/Stained_0S1.fcs", "BL1-H")
rac_1S1 <- process("../data/FCS/EAM_20190403_MURI_10day/Specimen1_1S2.fcs", "BL1-H")
rac_2S1 <- process("../data/FCS/EAM_20190403_MURI_100day/Stained_2S1-1.fcs", "BL1-H")
opar <- par(no.readonly = TRUE)
par(mar = c(5,6,4,2)+0.1)
plot(rac_0S1[,1], log(rac_0S1[,2]), type = 'p', axes = F, xlab = "Rank in activity", ylab = "", main = "Absolute", las = 1, cex.lab = 1.4, cex.axis = 1.25)
mtext("log(RSG-H value)", side = 2, line = 3, cex.lab = 1.4)
points(rac_1S1[,1], log(rac_1S1[,2]), type = 'p', col = "red")
points(rac_2S1[,1], log(rac_2S1[,2]), type = 'p', col = "blue")

box()
axis(side = 1, labels = T, cex.axis = 1.25)
axis(side = 2, las = 1, cex.axis = 1.25)

par <- opar
```


```{r}
# Cdist_0S1 <- CDist(rac_0S1[,2])
# pareto_0S1 <- fitdist(as.vector(Cdist_0S1[,2]), "pareto", start = list(shape = 0.1, scale = 10))
# lognorm_0S1 <- fitdist(as.vector(Cdist_0S1[,2]), "lnorm")
# Cdist_1S1 <- CDist(rac_1S1[,2])
# pareto_1S1 <- fitdist(as.vector(Cdist_1S1[,2]), "pareto", start = list(shape = 0.1, scale = 10))
# lognorm_1S1 <- fitdist(as.vector(Cdist_1S1[,2]), "lnorm")
# Cdist_2S1 <- CDist(rac_2S1[,2])
# pareto_2S1 <- fitdist(as.vector(Cdist_2S1[,2]), "pareto", start = list(shape = 0.1, scale = 10))
# lognorm_2S1 <- fitdist(as.vector(Cdist_2S1[,2]), "lnorm")

Cdist_0S1 <- CDist(rac_0S1[,2])
pareto_0S1 <- fitdist(rac_0S1[,2], "pareto", start = list(shape = 0.1, scale = 10))
lognorm_0S1 <- fitdist(rac_0S1[,2], "lnorm")
Cdist_1S1 <- CDist(rac_1S1[,2])
pareto_1S1 <- fitdist(rac_1S1[,2], "pareto", start = list(shape = 0.1, scale = 10))
lognorm_1S1 <- fitdist(rac_1S1[,2], "lnorm")
Cdist_2S1 <- CDist(rac_2S1[,2])
pareto_2S1 <- fitdist(rac_2S1[,2], "pareto", start = list(shape = 0.1, scale = 10))
lognorm_2S1 <- fitdist(rac_2S1[,2], "lnorm")

# par(mar = c(5,5,4,1)+0.1, mfrow = c(1,2))
# 
# plot(rac_0S1[,1], log(rac_0S1[,2]), type = 'p', axes = F, xlab = "Rank in activity", ylab = "", las = 1, cex.lab = 1.4, cex.axis = 1.25)
# mtext("log(RSG-H value)", side = 2, line = 3, cex = 1.4)
# points(rac_1S1[,1], log(rac_1S1[,2]), type = 'p', col = "red")
# points(rac_2S1[,1], log(rac_2S1[,2]), type = 'p', col = "blue")
# 
# box()
# axis(side = 1, labels = T, cex.axis = 1.25)
# axis(side = 2, las = 1, cex.axis = 1.25)

# par <- opar
# 
# plot(log(Cdist_0S1[,2]),log(Cdist_0S1[,1]), type = 'p', axes = F, xlab = "", ylab = "", las = 1, cex.lab = 1.4, cex.axis = 1.25)
# mtext("% of rank-ordered cells \n contributing to activity", side = 1, line = 4, cex = 1.4)
# mtext("Cumulative % RSG activity", side = 2, line = 3, cex = 1.4)
# points(log(Cdist_1S1[,2]), log(Cdist_1S1[,1]), type = 'p', col = "red")
# points(log(Cdist_2S1[,2]), log(Cdist_2S1[,1]), type = 'p', col = "blue")
# 
# box()
# axis(side = 1, labels = T, cex.axis = 1.25)
# axis(side = 2, las = 1, cex.axis = 1.25)
# 
# par <- opar

cdfcomp(list(pareto_2S1, lognorm_2S1), xlogscale = FALSE, ylogscale = FALSE)
```
```{r}

S1_0_fits <- as.data.frame(t(rac_0S1[,2]))
S1_1_fits <- as.data.frame(t(rac_1S1[,2]))
S1_2_fits <- as.data.frame(t(rac_2S1[,2]))
S1_0_RACfit <- radfit(S1_0_fits)
S1_0_RACfit
S1_1_RACfit <- radfit(S1_1_fits)
S1_1_RACfit
S1_2_RACfit <- radfit(S1_2_fits)
S1_2_RACfit
plot(S1_0_RACfit, las=1, cex.lab = 1.4, cex.axis = 1.25)
plot(S1_1_RACfit, las = 1, cex.lab = 1.4, cex.axis = 1.25)
plot(S1_2_RACfit, las = 1, cex.lab = 1.4, cex.axis = 1.25)

```

```{r}
hist_0S1 <- hist(rac_0S1[,2], breaks = 30)
hist_1S1 <- hist(rac_1S1[,2], breaks = 30)
hist_2S1 <- hist(rac_2S1[,2], breaks = 30)
#plot(log(hist_0S1$mids), log(hist_0S1$density))
points(log(hist_1S1$mids), log(hist_1S1$density), col = "red")
#points(log(hist_2S1$mids), log(hist_2S1$density), col = "blue")
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
hist <- hist(rac_C1)
hist.dat <- data.frame(hist$mids,hist$counts,hist$density)
colnames(hist.dat)<- c("mids", "counts", "density")
plot(log10(hist.dat$mids), log10(hist.dat$density))
```
